---
title: "Chip Design in India: Fabless Firms & GCC Design Centres"
subtitle: "Tracking Indian fabless companies and global semiconductor design operations in India"
date: last-modified
---

```{r setup, include=FALSE}
source("R/helpers.R")
library(leaflet)
library(DT)

firms <- load_design_firms("data/design.yml")
locations <- load_design_locations("data/design.yml")
```

## Overview

India's semiconductor story is not just about manufacturing. Long before the first fab broke ground, India had become one of the world's largest bases for chip *design*. Global semiconductor companies have operated R&D centres in India for decades, and a growing cohort of Indian fabless startups is now designing chips from scratch.

This page tracks three distinct groups:

- **Indian fabless firms** — companies headquartered in India that design their own chips (including beneficiaries of the Design Linked Incentive scheme)
- **GCC design centres** — India R&D operations of global semiconductor companies that design chips
- **EDA & IP providers** — companies that build the tools and IP blocks used by chip designers (not chip designers themselves)

They have different strategic implications. Indian fabless firms build domestic IP ownership; GCCs bring design expertise, talent pipelines, and integration into global supply chains; EDA & IP providers underpin the entire design ecosystem. All matter, but differently.

As of `r format(Sys.Date(), "%B %Y")`, this tracker covers **`r sum(firms$category %in% c("Indian Fabless", "DLI Beneficiary"))` Indian fabless firms**, **`r sum(firms$category == "GCC Design Centre")` GCC design centres**, and **`r sum(firms$category == "EDA & IP Provider")` EDA & IP providers** across **`r length(unique(firms$states))`** states.

---

## Design Centre Map

```{r map, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6}
locations$colour <- sapply(locations$category, design_category_color)

m <- leaflet(locations, width = "100%") %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  setView(lng = 78.5, lat = 20, zoom = 5) %>%
  addCircleMarkers(
    lng = ~lon, lat = ~lat,
    radius = 7,
    color = ~colour,
    fillColor = ~colour,
    fillOpacity = 0.7,
    stroke = TRUE,
    weight = 1,
    label = ~lapply(paste0("<strong>", name, "</strong><br/>", city, " | ", product_focus), htmltools::HTML),
    popup = ~paste0(
      '<div class="facility-popup">',
      '<h4>', name, '</h4>',
      '<div class="popup-row">', sapply(category, design_category_badge), '</div>',
      '<div class="popup-row"><span class="popup-label">City:</span> ', city, '</div>',
      '<div class="popup-row"><span class="popup-label">Focus:</span> ', product_focus, '</div>',
      '<div class="popup-row"><span class="popup-label">Scope:</span> ', design_scope, '</div>',
      '</div>'
    ),
    clusterOptions = markerClusterOptions(
      showCoverageOnHover = FALSE,
      maxClusterRadius = 40,
      spiderfyOnMaxZoom = TRUE
    )
  ) %>%
  addLegend(
    position = "bottomright",
    colors = sapply(c("Indian Fabless", "DLI Beneficiary", "GCC Design Centre", "EDA & IP Provider"), design_category_color),
    labels = c("Indian Fabless", "DLI Beneficiary", "GCC Design Centre", "EDA & IP Provider"),
    title = "Category",
    opacity = 0.8
  )

m
```

---

## Indian Fabless Firms

Design capability is scored on four dimensions (each 1–5): **IP Ownership** (licensed cores → fully custom architecture), **Design Completeness** (single block → full chip tapeout), **Domain Difficulty** (commodity digital → custom analog/RF/GPU), and **Market Readiness** (pre-silicon → volume production). The composite is their equal-weighted average. Firms not yet scored show "—".

```{r indian-table, echo=FALSE, warning=FALSE, message=FALSE}
indian <- firms %>%
  filter(category %in% c("Indian Fabless", "DLI Beneficiary")) %>%
  mutate(
    Name = name,
    Category = sapply(category, design_category_badge),
    Focus = product_focus,
    Score = sapply(design_composite, design_score_bar_html),
    Scope = design_scope,
    Node = node_sophistication,
    `Founded` = founded,
    Locations = cities
  ) %>%
  select(Name, Category, Focus, Score, Scope, Node, Founded, Locations)

DT::datatable(
  indian,
  escape = FALSE,
  rownames = FALSE,
  options = list(
    pageLength = 25,
    dom = 'ftip',
    order = list(list(0, 'asc')),
    columnDefs = list(
      list(className = 'dt-left', targets = '_all')
    )
  ),
  class = "display compact stripe"
)
```

---

## GCC Design Centres

GCC design centres are scored differently: **Strategic Depth** (cost centre → India-led product decisions), **Design Completeness** (verification only → full chip tapeout from India), **Domain Difficulty** (same as above), and **India Scale** (headcount: <500 → >10,000).

```{r gcc-table, echo=FALSE, warning=FALSE, message=FALSE}
gcc <- firms %>%
  filter(category == "GCC Design Centre") %>%
  mutate(
    Name = name,
    Parent = paste0(parent_company, " (", parent_hq, ")"),
    Focus = product_focus,
    Score = sapply(design_composite, design_score_bar_html),
    Scope = design_scope,
    Node = node_sophistication,
    `Est.` = founded,
    `Headcount` = ifelse(is.na(india_headcount), "—", paste0("~", format(india_headcount, big.mark = ","))),
    Locations = cities
  ) %>%
  select(Name, Parent, Focus, Score, Scope, Node, Est., Headcount, Locations)

DT::datatable(
  gcc,
  escape = FALSE,
  rownames = FALSE,
  options = list(
    pageLength = 25,
    dom = 'ftip',
    order = list(list(6, 'desc')),
    columnDefs = list(
      list(className = 'dt-left', targets = '_all')
    )
  ),
  class = "display compact stripe"
)
```

---

## EDA & IP Providers

These are not chip design firms — they build the electronic design automation (EDA) tools and semiconductor IP blocks that chip designers use. Their India operations are massive, often among the largest R&D centres outside the US, and they train a significant share of India's semiconductor design workforce.

```{r eda-table, echo=FALSE, warning=FALSE, message=FALSE}
eda <- firms %>%
  filter(category == "EDA & IP Provider") %>%
  mutate(
    Name = name,
    Parent = paste0(parent_company, " (", parent_hq, ")"),
    Focus = product_focus,
    Scope = design_scope,
    Node = node_sophistication,
    `Est.` = founded,
    `Headcount` = ifelse(is.na(india_headcount), "—", paste0("~", format(india_headcount, big.mark = ","))),
    Locations = cities
  ) %>%
  select(Name, Parent, Focus, Scope, Node, Est., Headcount, Locations)

DT::datatable(
  eda,
  escape = FALSE,
  rownames = FALSE,
  options = list(
    pageLength = 10,
    dom = 'ftip',
    order = list(list(0, 'asc')),
    columnDefs = list(
      list(className = 'dt-left', targets = '_all')
    )
  ),
  class = "display compact stripe"
)
```

---

## City-wise Concentration

```{r city-chart, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4}
library(ggplot2)

city_counts <- locations %>%
  count(city, category) %>%
  arrange(desc(n))

ggplot(city_counts, aes(x = reorder(city, n, sum), y = n, fill = category)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = c(
    "Indian Fabless" = "#E65100",
    "DLI Beneficiary" = "#2E7D32",
    "GCC Design Centre" = "#1565C0",
    "EDA & IP Provider" = "#6A1B9A"
  )) +
  labs(
    title = "Semiconductor Design Centres by City",
    x = NULL, y = "Number of centres",
    fill = "Category"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold")
  )
```

---

::: {.callout-note}
## Data Coverage & Sources

This tracker is a work in progress. We aim to cover all DLI beneficiaries (~30 firms) and major GCC design centres (~15-20). If you know of a firm or centre that should be listed, please [open a GitHub Issue](https://github.com/pranaykotas/india-semiconductor-tracker/issues/new/choose) or [submit via our form](https://forms.gle/FDESu4jRksmr7FTk7).

Primary sources: MeitY DLI scheme announcements, company websites, IESA reports, press releases.
:::
