---
title: "Equipment & Materials"
subtitle: "Tracking semiconductor equipment, gases, chemicals, and materials investments in India"
date: last-modified
---

```{r setup, include=FALSE}
source("R/helpers.R")
library(leaflet)
library(DT)
library(sf)
library(ggplot2)

equip <- load_equipment("data/equipment_materials.yml")
```

## Overview

Semicon 2.0 — India's ₹1.27 lakh crore semiconductor programme approved in July 2026 — explicitly names **equipment and materials** as one of six pillars, alongside chip design, fabrication, advanced packaging, R&D, and talent. This is the supply chain that feeds every fab and OSAT tracked elsewhere on this site: the machines that deposit, etch, and pattern silicon, and the gases, chemicals, and substrates those machines consume.

This page tracks equipment makers, gas and chemical suppliers, materials and substrate producers, and infrastructure/process-engineering firms with a **concrete India investment or facility of their own** — not merely a company that has signed a supply agreement with a tracked fab (those relationships are recorded as milestones on the buyer's own facility page, e.g. Tata Electronics' Dholera fab page lists its ASML, FUJIFILM, and Kelington MoUs).

As of `r format(Sys.Date(), "%B %Y")`, this tracker covers **`r nrow(equip)` firms** across **`r length(unique(equip$state))`** states, representing **`r format(sum(equip$investment_inr, na.rm = TRUE), big.mark = ",")` crore** in disclosed rupee-denominated investment plus **$`r format(sum(equip$investment_usd_m, na.rm = TRUE), big.mark = ",")`M** in dollar-denominated commitments.

::: {.callout-note}
This is a new, early-stage tracker (added September 2026) — coverage will grow as more equipment/materials investments are announced and researched. If you know of a firm that should be listed, please [open a GitHub Issue](https://github.com/pranaykotas/india-semiconductor-tracker/issues/new/choose) or [submit via our form](https://forms.gle/FDESu4jRksmr7FTk7).
:::

---

## Equipment & Materials Map

```{r map, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6}
equip$colour <- sapply(equip$category, equipment_category_color)
india <- st_read("data/shp/datameet/india-composite.geojson", quiet = TRUE)

carto_key <- Sys.getenv("CARTO_API_KEY")
positron_url <- paste0(
  "https://basemaps.cartocdn.com/rastertiles/light_all/{z}/{x}/{y}.png?key=",
  carto_key
)

m <- leaflet(equip, width = "100%", options = leafletOptions(minZoom = 4, maxZoom = 10)) %>%
  addTiles(
    urlTemplate = positron_url,
    attribution = '&copy; <a href="https://carto.com/attributions">CARTO</a>, &copy; <a href="https://www.openstreetmap.org/copyright">OpenStreetMap</a> contributors'
  ) %>%
  fitBounds(lng1 = 68, lat1 = 7, lng2 = 97, lat2 = 36) %>%
  addPolygons(
    data = india,
    color = "#620d3c",
    weight = 2,
    fillColor = "#E8EAF0",
    fillOpacity = 0.1,
    group = "Official Boundary"
  ) %>%
  addCircleMarkers(
    lng = ~lon, lat = ~lat,
    radius = 8,
    color = "#ffffff",
    fillColor = ~colour,
    fillOpacity = 0.85,
    stroke = TRUE,
    weight = 1.5,
    label = ~lapply(paste0("<strong>", name, "</strong><br/>", city, " | ", category), htmltools::HTML),
    popup = ~paste0(
      '<div class="facility-popup">',
      '<h4>', name, '</h4>',
      '<div class="popup-row">', sapply(category, equipment_category_badge), '</div>',
      '<div class="popup-row"><span class="popup-label">City:</span> ', city, '</div>',
      '<div class="popup-row"><span class="popup-label">Status:</span> ', sapply(status, status_badge_html), '</div>',
      '<div class="popup-row"><span class="popup-label">Investment:</span> ', mapply(format_equipment_investment, investment_inr, investment_usd_m), '</div>',
      '<div class="popup-row" style="margin-top:6px;"><a href="equipment-firms/', id, '.html" class="btn-detail">Full Profile →</a></div>',
      '</div>'
    ),
    clusterOptions = markerClusterOptions(
      showCoverageOnHover = FALSE,
      maxClusterRadius = 40,
      disableClusteringAtZoom = 9
    )
  ) %>%
  addLegend(
    position = "bottomright",
    colors = sapply(c("Equipment Manufacturer", "Gases & Chemicals", "Materials & Substrates", "Infrastructure & Services"), equipment_category_color),
    labels = c("Equipment Manufacturer", "Gases & Chemicals", "Materials & Substrates", "Infrastructure & Services"),
    title = "Category",
    opacity = 0.8
  )

m
```

---

## All Firms

```{r table, echo=FALSE, warning=FALSE, message=FALSE}
tbl <- equip %>%
  mutate(
    Name = paste0('<a href="equipment-firms/', id, '.html">', name, '</a>'),
    Category = sapply(category, equipment_category_badge),
    Parent = ifelse(is.na(parent_company), "Indian-origin", paste0(parent_company, " (", parent_hq, ")")),
    Status = sapply(status, status_badge_html),
    Investment = mapply(format_equipment_investment, investment_inr, investment_usd_m),
    Location = paste0(city, ", ", state),
    Supplies = ifelse(supplies_to == "", "General / not facility-specific", supplies_to)
  ) %>%
  select(Name, Category, Parent, Status, Investment, Location, Supplies)

DT::datatable(
  tbl,
  escape = FALSE,
  rownames = FALSE,
  options = list(
    pageLength = 25,
    dom = 'ftip',
    order = list(list(0, 'asc')),
    columnDefs = list(
      list(className = 'dt-left', targets = '_all')
    )
  ),
  class = "display compact stripe"
)
```

---

## By Category

```{r category-chart, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5}
cat_counts <- equip %>% count(category)

ggplot(cat_counts, aes(x = reorder(category, n), y = n, fill = category)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = c(
    "Equipment Manufacturer"    = "#620d3c",
    "Gases & Chemicals"         = "#1565C0",
    "Materials & Substrates"    = "#2f6b4a",
    "Infrastructure & Services" = "#f1a222"
  )) +
  labs(title = NULL, x = NULL, y = "Number of firms") +
  theme_minimal() +
  theme(legend.position = "none")
```

---

::: {.callout-note}
## Data Coverage & Sources

This tracker only includes firms with their own disclosed India investment or facility — not every company that has signed a supply MoU with a tracked fab or OSAT (those appear as milestones on that facility's own page instead). Coverage is expected to grow significantly as Semicon 2.0's equipment-and-materials pillar matures.

Primary sources: company press releases, SEMICON India event coverage, and business press reporting.
:::
