---
title: "India Semiconductor Tracker: Commercial & Research Facilities"
subtitle: "Tracking commercial volume production units and strategic research fabs"
date: last-modified
---

```{r setup, include=FALSE}
source("R/helpers.R")
library(leaflet)
library(DT)
library(ggplot2)
library(scales)
library(sf)
library(rnaturalearth)

facilities <- load_facilities("data/facilities.yml")
```

## The Story So Far

India imports nearly all its semiconductor chips — a vulnerability exposed by the global chip shortage of 2020-21. In response, the government launched the **India Semiconductor Mission (ISM)** with an initial outlay of ₹76,000 crore to build domestic manufacturing capacity.

As of `r format(Sys.Date(), "%B %Y")`, **`r sum(facilities$status == "Operational" & facilities$category == "Commercial (ISM Approved)")` of `r sum(facilities$category == "Commercial (ISM Approved)")` approved commercial facilities are now operational**. India's first fab — the Tata-PSMC plant at Dholera — is under construction. Total approved investment across all ISM projects stands at **₹`r format(sum(facilities$investment_inr[facilities$category == "Commercial (ISM Approved)"], na.rm = TRUE), big.mark = ",")` crore** across **`r length(unique(facilities$state[facilities$category == "Commercial (ISM Approved)"]))`** states.

But the hard part is just beginning. Assembly and packaging projects are moving fast, but [the budget data shows](budget.qmd) a significant gap between allocated funds and actual disbursement — especially for fabrication. India's fab ambitions target [mature 28nm-55nm nodes](nodes.qmd), a deliberate strategic choice that avoids the cutting edge but addresses the chips India actually needs.

This tracker monitors every facility in real time. Explore the map below, or dive into the [timeline](timeline.qmd), [technology context](nodes.qmd), or [budget analysis](budget.qmd).

---

## Recent Developments

```{r recent-developments, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
# Pull the most recent milestones across all facilities from YAML
raw_facs <- yaml::read_yaml("data/facilities.yml")$facilities
all_milestones <- do.call(rbind, lapply(raw_facs, function(f) {
  if (is.null(f$milestones)) return(NULL)
  do.call(rbind, lapply(f$milestones, function(m) {
    data.frame(
      facility = f$name,
      id = f$id,
      date = as.Date(m$date),
      event = m$event,
      stringsAsFactors = FALSE
    )
  }))
}))

# Show the 5 most recent milestones
recent <- all_milestones[order(all_milestones$date, decreasing = TRUE), ]
recent <- head(recent, 5)

for (i in seq_len(nrow(recent))) {
  r <- recent[i, ]
  date_label <- format(r$date, "%b %Y")
  cat(sprintf("- **%s** — %s ([%s](facilities/%s.html))\n",
              date_label, r$event, r$facility, r$id))
}
```

---

## Facility Map

Commercial facilities approved under the **India Semiconductor Mission (ISM)** are coloured by type. Strategic and academic research fabs are marked in [**Slate Grey**]{style="color:#455A64"}. Non-ISM OSAT projects are in [**Teal**]{style="color:#00796B"}.

```{r map, echo=FALSE, warning=FALSE, message=FALSE}
# Build colour vector, popups, and labels
colors <- mapply(type_color, facilities$type, facilities$category, USE.NAMES = FALSE)
popups <- vapply(1:nrow(facilities), function(i) make_popup(facilities[i, ]), character(1))
labels <- lapply(1:nrow(facilities), function(i) htmltools::HTML(make_label(facilities[i, ])))

# Get official India boundary overlay (DataMeet composite GeoJSON)
india <- st_read("data/shp/datameet/india-composite.geojson", quiet = TRUE)

# Use CartoDB.Positron for a reliable base map and overlay DataMeet boundaries
leaflet(facilities, options = leafletOptions(minZoom = 4, maxZoom = 10)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  fitBounds(lng1 = 68, lat1 = 7, lng2 = 97, lat2 = 36) %>%
  addPolygons(
    data = india,
    color = "#0D1F3C",
    weight = 2,
    fillColor = "#E8EAF0",
    fillOpacity = 0.1,
    group = "Official Boundary"
  ) %>%
  addCircleMarkers(
    lng = ~lon, lat = ~lat,
    radius = 10,
    color = colors,
    fillColor = colors,
    fillOpacity = 0.8,
    stroke = TRUE,
    weight = 1.5,
    popup = popups,
    label = labels,
    labelOptions = labelOptions(
      style = list("font-size" = "12px", "padding" = "6px 10px"),
      direction = "auto"
    ),
    clusterOptions = markerClusterOptions(
      maxClusterRadius = 30,
      spiderfyOnMaxZoom = TRUE,
      showCoverageOnHover = FALSE,
      zoomToBoundsOnClick = TRUE
    )
  ) %>%
  addLegend(
    position = "bottomright",
    colors = c("#C62828", "#1565C0", "#6A1B9A", "#00796B", "#455A64"),
    labels = c("Commercial Fab", "Assembly & Packaging", "Compound Semiconductor", "OSAT (Non-ISM)", "Research & Strategic"),
    title = "Facility Category"
  )
```

## Summary: Commercial Units (ISM Approved)

::: {.grid}
::: {.g-col-12 .g-col-sm-6 .g-col-md-3}
::: {.summary-card}
[`r sum(facilities$category == "Commercial (ISM Approved)")`]{.card-value}
[Commercial units]{.card-label}
:::
:::

::: {.g-col-12 .g-col-sm-6 .g-col-md-3}
::: {.summary-card}
[`r paste0("\u20b9", format(sum(facilities$investment_inr, na.rm = TRUE), big.mark = ","))`]{.card-value}
[Planned investment (crore)]{.card-label}
:::
:::

::: {.g-col-12 .g-col-sm-6 .g-col-md-3}
::: {.summary-card}
[`r sum(facilities$category == "Research & Strategic")`]{.card-value}
[Research/Strategic fabs]{.card-label}
:::
:::

::: {.g-col-12 .g-col-sm-6 .g-col-md-3}
::: {.summary-card}
[`r sum(facilities$status == "Operational" & facilities$category == "Commercial (ISM Approved)")`]{.card-value}
[Operational (Commercial)]{.card-label}
:::
:::
:::

## Planned Investment by Facility Type (Commercial)

```{r chart-type, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4, dev="ragg_png"}
type_data <- facilities %>%
  filter(category == "Commercial (ISM Approved)") %>%
  group_by(type) %>%
  summarise(
    total_inr = sum(investment_inr, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

type_colors <- c(
  "Fab"                    = "#C62828",
  "Assembly & Packaging"   = "#1565C0",
  "Compound Semiconductor" = "#6A1B9A"
)

ggplot(type_data, aes(x = reorder(type, total_inr), y = total_inr, fill = type)) +
  geom_col(width = 0.6) +
  geom_text(
    aes(label = paste0(n, " unit", ifelse(n == 1, "", "s"), "\n\u20b9", format(total_inr, big.mark = ","), " cr")),
    hjust = -0.1, size = 3.5, color = "#333"
  ) +
  coord_flip() +
  scale_fill_manual(values = type_colors, guide = "none") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.45))) +
  labs(x = NULL, y = "Total Planned Investment (INR crore)") +
  theme_minimal() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 11)
  )
```

## All Facilities

```{r table, echo=FALSE, warning=FALSE, message=FALSE}
table_data <- facilities %>%
  mutate(
    Name = paste0('<a href="facilities/', id, '.html">', name, '</a>'),
    Status = mapply(status_badge_html, status, status_detail),
    Complexity = sapply(complexity_score, complexity_bar_html),
    Slippage = sapply(slippage_months, slippage_badge_html),
    Investment = mapply(format_investment, investment_inr, category, MoreArgs = list(short = TRUE)),
    Location = paste0(city, ", ", state)
  ) %>%
  select(
    Name,
    Type = type,
    Capability = capability,
    Complexity,
    Investment,
    Status,
    Slippage,
    Location
  )

datatable(
  table_data,
  escape = FALSE,
  filter = "top",
  options = list(
    pageLength = 15,
    dom = "ftip",
    scrollX = TRUE,
    columnDefs = list(
      list(className = "dt-center", targets = c(3, 5, 6))
    ),
    initComplete = JS("
      function(settings, json) {
        var wrapper  = settings.nTableWrapper;
        var $body    = $(wrapper).find('.dataTables_scrollBody');
        var $scroll  = $(wrapper).find('.dataTables_scroll');
        if ($body.length === 0) return;

        // --- top scroll bar ---
        var $top = $('<div class=\"dt-top-scroll\"><div class=\"dt-top-scroll-inner\"></div></div>');
        $scroll.before($top);
        setTimeout(function() {
          $top.find('.dt-top-scroll-inner').css('width', $body[0].scrollWidth + 'px');
        }, 150);
        $top.on('scroll', function() { $body.scrollLeft($top.scrollLeft()); });
        $body.on('scroll', function() { $top.scrollLeft($body.scrollLeft()); });

        // --- drag to scroll ---
        var dragging = false, startX, startLeft;
        $body.css('cursor', 'grab');
        $body
          .on('mousedown', function(e) {
            dragging = true;
            startX   = e.clientX;
            startLeft = $body.scrollLeft();
            $body.css({'cursor': 'grabbing', 'user-select': 'none'});
          })
          .on('mouseup mouseleave', function() {
            if (!dragging) return;
            dragging = false;
            $body.css({'cursor': 'grab', 'user-select': ''});
          })
          .on('mousemove', function(e) {
            if (!dragging) return;
            e.preventDefault();
            $body.scrollLeft(startLeft - (e.clientX - startX));
          });
      }
    ")
  ),
  rownames = FALSE,
  class = "display compact"
)
```

::: {.callout-note}
## Understanding the Metrics
- **Technical Complexity:** A weighted score combining **Technical Difficulty (55%)** and **Capital Intensity (45%)**. Benchmarked against a 3nm fab (5/5).
- **Slippage:** The delay in months calculated from the *original* announced/expected completion date compared to the current actual or expected date.
:::

::: {.callout-note}
## Complexity Index
Scores are benchmarked against a **cutting-edge 3nm fab** (e.g. TSMC Arizona) which would score **5/5** on all three dimensions — technology difficulty, foreign dependence, and capital intensity. India's current projects are substantially less complex than that frontier. A 28nm fab scores ~2.9/5; standard assembly and packaging facilities score ~1–1.5/5. See the [About page](about.qmd) for full methodology.
:::

::: {.callout-note}
## Data Source
Data from the [SEMICON India 2025 government factsheet](https://www.pib.gov.in/PressReleasePage.aspx?PRID=2128468) (September 2025) and PIB press releases.
:::

::: {.callout-tip}
## Have an update?
Know about a status change, a new announcement, or a correction? **[Submit an update via our form](https://forms.gle/FDESu4jRksmr7FTk7)** — it takes 2 minutes, no account required. Or **[open a GitHub Issue](https://github.com/pranaykotas/india-semiconductor-tracker/issues/new/choose)** for detailed contributions.
:::
