---
title: "Project Timeline"
subtitle: "Milestones and expected completion dates for India's semiconductor facilities"
date: last-modified
---

```{r setup, include=FALSE}
source("R/helpers.R")
library(DT)
library(ggplot2)
library(scales)
library(dplyr)
library(tidyr)

facilities <- load_facilities("data/facilities.yml")
```

## Facility Timelines

Each row represents a facility. **Bars** show the span from construction start (or announcement, if construction hasn't begun) to expected or actual completion. **Diamond markers (◆)** mark the announcement date. **Vertical ticks (|)** show the original target completion date where known. The **dashed line** marks today.

Research and strategic facilities (SCL Mohali, GAETEC, IISc MNNFC) predate the ISM timeline and are not shown here — see the [main table](index.qmd) for the full list.

```{r gantt-chart, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=7, dev="ragg_png"}
# Filter to ISM-era facilities (post-2023 announcements)
gantt_data <- facilities %>%
  filter(!is.na(date_announced), date_announced >= as.Date("2023-01-01")) %>%
  mutate(
    bar_start = coalesce(date_construction, date_announced),
    bar_end = coalesce(date_completion, date_original_expect, Sys.Date()),
    has_construction = !is.na(date_construction),
    # Short labels for y-axis
    name_label = gsub(" Semiconductor| Facility| Campus", "", name),
    type = factor(type, levels = c("Fab", "Assembly & Packaging", "Compound Semiconductor"))
  ) %>%
  arrange(type, date_announced)

# Status colours matching site palette
status_colors <- c(
  "Operational"        = "#2f6b4a",
  "Under Construction" = "#1565C0",
  "Approved"           = "#f1a222",
  "Announced"          = "#8C8480"
)

# Build the Gantt chart
p <- ggplot(gantt_data, aes(y = reorder(name_label, desc(date_announced)))) +
  # Dashed bars for facilities not yet under construction
  geom_segment(
    data = filter(gantt_data, !has_construction),
    aes(x = bar_start, xend = bar_end,
        yend = reorder(name_label, desc(date_announced)),
        color = status),
    linewidth = 5, lineend = "round", linetype = "dashed", alpha = 0.5
  ) +
  # Solid bars for facilities under construction or completed
  geom_segment(
    data = filter(gantt_data, has_construction),
    aes(x = bar_start, xend = bar_end,
        yend = reorder(name_label, desc(date_announced)),
        color = status),
    linewidth = 5, lineend = "round"
  ) +
  # Original target tick marks (where known and different from bar_end)
  geom_point(
    data = filter(gantt_data, !is.na(date_original_expect)),
    aes(x = date_original_expect,
        y = reorder(name_label, desc(date_announced))),
    shape = "|", size = 4, color = "#620d3c"
  ) +
  # Diamond markers for announcement date
  geom_point(
    aes(x = date_announced, color = status),
    shape = 18, size = 3.5
  ) +
  # Today line
  geom_vline(xintercept = as.numeric(Sys.Date()),
             linetype = "dashed", color = "#620d3c", linewidth = 0.4) +
  annotate("text", x = Sys.Date(), y = Inf, label = "Today",
           hjust = -0.15, vjust = 1.5, size = 3, color = "#620d3c",
           fontface = "italic") +
  # Facet by facility type
  facet_grid(type ~ ., scales = "free_y", space = "free_y", switch = "y") +
  # Status colours
  scale_color_manual(values = status_colors, name = "Status") +
  scale_x_date(
    date_breaks = "6 months", date_labels = "%b '%y",
    limits = c(as.Date("2023-01-01"), max(gantt_data$bar_end) + 120)
  ) +
  labs(x = NULL, y = NULL,
       title = "Semiconductor Facility Timelines",
       subtitle = "Solid bars = under construction or complete. Dashed = planned. ◆ = announced. | = original target.") +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text.y.left = element_text(face = "bold", size = 10, color = "#620d3c", angle = 0),
    strip.placement = "outside",
    plot.title = element_text(face = "bold", size = 14, color = "#620d3c"),
    plot.subtitle = element_text(size = 9.5, color = "#666", margin = margin(b = 12)),
    legend.position = "top",
    axis.text.y = element_text(size = 9),
    axis.text.x = element_text(size = 9),
    plot.margin = margin(10, 20, 10, 10)
  )

p
```

## Key Dates

```{r dates-table, echo=FALSE, warning=FALSE, message=FALSE}
dates_data <- facilities %>%
  mutate(
    Announced    = format(date_announced, "%d %b %Y"),
    Approved     = ifelse(is.na(date_approved), "—", format(date_approved, "%d %b %Y")),
    `Const. Start` = ifelse(is.na(date_construction), "TBD", format(date_construction, "%d %b %Y")),
    `Orig. Target` = ifelse(is.na(date_original_expect), "TBD", format(date_original_expect, "%b %Y")),
    `Curr. Target` = ifelse(is.na(date_completion), "TBD", format(date_completion, "%b %Y")),
    Status = mapply(status_badge_html, status, status_detail)
  ) %>%
  select(Facility = name, Type = type, Announced, Approved, `Const. Start`, `Orig. Target`, `Curr. Target`, Status)

datatable(
  dates_data,
  escape = FALSE,
  options = list(pageLength = 15, dom = "t", ordering = TRUE),
  rownames = FALSE,
  class = "display compact"
)
```

## Source Library

Primary sources and official government announcements.

```{r sources-library, echo=FALSE, warning=FALSE, message=FALSE}
# Read YAML directly to ensure we get all sources
raw_data <- yaml::read_yaml("data/facilities.yml")$facilities
sources_list <- lapply(raw_data, function(f) {
  if (is.null(f$sources)) return(NULL)
  lapply(f$sources, function(s) {
    tibble(
      Facility = f$name,
      Date = as.Date(s$date),
      Source = paste0('<a href="', s$url, '" target="_blank">', s$title, '</a>')
    )
  }) %>% bind_rows()
}) %>% bind_rows()

if (!is.null(sources_list) && nrow(sources_list) > 0) {
  sources_list %>%
    arrange(desc(Date)) %>%
    datatable(
      escape = FALSE,
      options = list(pageLength = 15, dom = "ftp"),
      rownames = FALSE,
      class = "display compact"
    )
} else {
  cat("No sources found.")
}
```
